Robertson and Cao Project

### 2024-04-17 code/analysis-code/analysis2.5.qmd
Analysis of rf and lasso completed
LASSO is complete, kinda, but we could also tune the penalty to F1 instead of roc_auc and see if this improves it. Also, we could try an elastic net model if we have time. Overall rf seems to have better performance. note: changes have not been rendered

---
title: "Data Analysis and Modeling of Teen Vaccination Surveys"
date: '`r format(Sys.Date())`'
Author: Kelly Cao and Rachel Robertson
output: html_document
editor: 
  markdown: 
    wrap: sentence
---
# Random Forest Model
```{r}
library(tidymodels) # use tidymodels framework.
library(ggplot2) # producing visual displays of data
library(dplyr) # manipulating and cleaning data
library(here) # making relative pathways
library(randomForest) # making random forest model
library(doParallel) # for parallel processing
library(rsample) # for cross validation
library(yardstick)
```

```{r}
# Load and preprocess data
data_location <- here::here("data","processed-data","cleandata1.rds")
mydata <- readRDS(data_location)

# Remove rows with missing values
mydata$SEX <- droplevels(mydata$SEX, exclude = c("DON'T KNOW", "MISSING IN ERROR", "REFUSED"))
mydata$INS_STAT2_I <- droplevels(mydata$INS_STAT2_I, exclude = "MISSING Data")
mydata$STATE <- droplevels(mydata$STATE, exclude = "Missing Data")
mydata$MOBIL_1 <- droplevels(mydata$MOBIL_1, exclude = c("DON'T KNOW", "MISSING IN ERROR", "REFUSED"))
mydata$FACILTY <- droplevels(mydata$FACILITY, exclude = "Missing Data")
mydata$P_UTDHPV <- droplevels(mydata$P_UTDHPV, exclude = "Missing Data")
```

```{r}
# Split data into training and testing datasets
set.seed(123) # seed for reproducibility
split_data <- initial_split(mydata, prop = 0.8) # 80% split for training/testing data
train_data <- training(split_data)
test_data <- testing(split_data)
```

```{r}
rf_rec <- recipe(P_UTDHPV ~ AGE + SEX + STATE + INS_STAT2_I + INCQ298A + INS_BREAK_I + INCPOV1 + RACEETHK + EDUC1 + LANGUAGE + MOBIL_1 + RENT_OWN + FACILITY, data = train_data) # use full model as recipe for the random forest model

@@

rf_fit <- rf_workflow%>%
  fit(data = train_data)%>% # use the workflow to fit the rf model to the data
print(rf_fit)
```
Now, I will examine the performance of the base random forest model.
```{r}
# Performance metrics of the first fit
rf_aug <- augment(rf_fit, train_data) # augment to make predictions for rf_fit

@@

Now, I will continue by tuning the RF model using cross validation. I start with a smaller numer of trees and lower number of folds because my computer cannot computationally handle many trees or folds.
```{r}
tune_spec <- 
  rand_forest(
    mtry = tune(), # parameters of random forest model to tune are the mtry, trees, and min_n
    trees = 100,
    min_n = tune()) %>% 
  set_engine("randomForest", seed = 123) %>% # make sure to set seed again for the tree
  set_mode("classification")

@@

# Stop parallel processing
stopImplicitCluster()
```
```{r}
# Find the best values for the tuned metrics, mtry and min_n
# find the ideal ROC_AUC metric for the rf tree
rf_res %>%
  collect_metrics() %>% # get metrics from the rf model created
  filter(.metric == "roc_auc") %>% # filter for the roc auc metric
  select(mean, min_n, mtry) %>% # select the columsn for mean, min_n and mtry
  pivot_longer(min_n:mtry,
    values_to = "value",
    names_to = "parameter"
  ) %>%
# Plot the ROC_AUC to find the ideal min_n and mtry
  ggplot(aes(value, mean, color = parameter)) +
  geom_point(show.legend = FALSE) +
  facet_wrap(~parameter, scales = "free_x") +
  labs(x = NULL, y = "AUC")
```
It seems that mtry is maximized between 100 and 150 and min_n is maximized between 1 and 5.
We can use a grid search to tune within a range to determine which is the ideal parameter value.

```{r}
# grid search tuning
rf_tune_grid <- grid_regular( #define a grid with a range for mtry and min_n
  mtry(range = c(100, 150)),
  min_n(range = c(1, 5)),
  levels = 6
)

@@

# Stop parallel processing
stopImplicitCluster()
```
From the plot, it seems that the ideal minimum node size (min_n) is 5 when the number of randomly selected predictors (mtry) is  140, when accuracy and ROC_AUC are both accounted for. We can check this using the select_best function.
```{r}
# Specify the metric and optimization criteria
best_auc <- select_best(rf_res2, metric = "roc_auc")

@@

# fit the tuned model
rf_rec <- recipe(P_UTDHPV ~ AGE + SEX + STATE + INS_STAT2_I + INCQ298A + INS_BREAK_I + INCPOV1 + RACEETHK + EDUC1 + LANGUAGE + MOBIL_1 + RENT_OWN + FACILITY, data = train_data) # use full model as recipe for the random forest model

rf_tune_workflow <- workflow() %>% # create workflow for rf model
  add_recipe(rf_rec)%>% # apply recipe
  add_model(final_rf) # apply model

rf_tune_fit <- rf_tune_workflow%>%
  fit(data = train_data)%>% # use the workflow to fit the rf model to the data
print(rf_fit)
```
The final random forest model was selected to optimize roc_auc, but it also has a fairly high accuracy. We can use
```{r}
# make predictions
rf_tuned_aug <- augment(rf_tune_fit, train_data)

@@

Now I will compare the model will the a single predictor model and the original fit to verify that there is improvement in the predicitons made.
```{r}
# RF model compared to single predictor model
## Create a single model
rf_rec_null <- recipe(P_UTDHPV ~ SEX, data = train_data) # specify the model with a recipe; I could not get a null model to work so I used one predictor as a minimal model for comparison

@@

# Get predictions from single predictor model
rf_null_aug <- augment(rf_fit_null, train_data)
```
Note to future self: You cannot plot the models on coordinates because the predictions are classifications (not coninuous). Find another visual representation to compare the models.

>>>>

---
title: "Data Analysis and Modeling of Teen Vaccination Surveys"
date: '`r format(Sys.Date())`'
Author: Kelly Cao and Rachel Robertson
output: html_document
editor: 
  markdown: 
    wrap: sentence
---
```{r, include=FALSE, cache=FALSE}
library(here)
knitr::read_chunk(here("./code/analysis-code/rf-tree.R"))
```

# Random Forest Model
```{r, message = FALSE, warning = FALSE}
library(tidymodels) # use tidymodels framework.
library(ggplot2) # producing visual displays of data
library(dplyr) # manipulating and cleaning data
library(here) # making relative pathways
library(randomForest) # making random forest model
library(doParallel) # for parallel processing
library(rsample) # for cross validation
library(yardstick) # performance metrics
library(vip) # visualize most important variables
```

```{r, message = FALSE, warning = FALSE}
# Load and preprocess data
data_location <- here::here("data","processed-data","cleandata1.rds")
mydata <- readRDS(data_location)

# Remove rows with missing values
mydata$SEX <- droplevels(mydata$SEX, exclude = c("DON'T KNOW", "MISSING IN ERROR", "REFUSED"))
mydata$INS_STAT2_I <- droplevels(mydata$INS_STAT2_I, exclude = "MISSING Data")
mydata$STATE <- droplevels(mydata$STATE, exclude = "Missing Data")
mydata$MOBIL_1 <- droplevels(mydata$MOBIL_1, exclude = c("DON'T KNOW", "MISSING IN ERROR", "REFUSED"))
mydata$FACILTY <- droplevels(mydata$FACILITY, exclude = "Missing Data")
mydata$P_UTDHPV <- droplevels(mydata$P_UTDHPV, exclude = "Missing Data")

```

```{r, message = FALSE, warning = FALSE}
# Split data into training and testing datasets
set.seed(123) # seed for reproducibility
split_data <- initial_split(mydata, prop = 0.8) # 80% split for training/testing data
train_data <- training(split_data)
test_data <- testing(split_data)
```

```{r, message = FALSE, warning = FALSE}
rf_rec <- recipe(P_UTDHPV ~ AGE + SEX + STATE + INS_STAT2_I + INCQ298A + INS_BREAK_I + INCPOV1 + RACEETHK + EDUC1 + LANGUAGE + MOBIL_1 + RENT_OWN + FACILITY, data = train_data) # use full model as recipe for the random forest model

@@

rf_fit <- rf_workflow%>%
  fit(data = train_data)%>% # use the workflow to fit the rf model to the data
  print(rf_fit)
```
Now, I will examine the performance of the base random forest model.
```{r, message = FALSE, warning = FALSE}
# Performance metrics of the first fit
rf_aug <- augment(rf_fit, train_data) # augment to make predictions for rf_fit

@@

Now, I will continue by tuning the RF model using cross validation. I start with a smaller numer of trees and lower number of folds because my computer cannot computationally handle many trees or folds.
```{r, message = FALSE, warning = FALSE}
tune_spec <- 
  rand_forest(
    mtry = tune(), # parameters of random forest model to tune are the mtry, trees, and min_n
    trees = 100,
    min_n = tune()) %>% 
  set_engine("randomForest", seed = 123) %>% # make sure to set seed again for the tree
  set_mode("classification")

@@

# Stop parallel processing
stopImplicitCluster()
```

```{r, message = FALSE, warning = FALSE}
rf_res %>%
  collect_metrics() %>% # get metrics from the rf model created
  filter(.metric == "roc_auc") %>% # filter for the roc auc metric
  select(mean, min_n, mtry) %>% # select the columsn for mean, min_n and mtry
  pivot_longer(min_n:mtry,
               values_to = "value",
               names_to = "parameter"
  ) %>%
  # Plot the ROC_AUC to find the ideal min_n and mtry
  ggplot(aes(value, mean, color = parameter)) +
  geom_point(show.legend = FALSE) +
  facet_wrap(~parameter, scales = "free_x") +
  labs(x = NULL, y = "AUC")
```
It seems that mtry is maximized between 100 and 150 and min_n is maximized between 1 and 5.
We can use a grid search to tune within a range to determine which is the ideal parameter value.

```{r, message = FALSE, warning = FALSE}
# grid search tuning
rf_tune_grid <- grid_regular( #define a grid with a range for mtry and min_n
  mtry(range = c(100, 150)),
  min_n(range = c(1, 5)),
  levels = 6
)

@@

# Stop parallel processing
stopImplicitCluster()
```
From the plot, it seems that the ideal minimum node size (min_n) is 5 when the number of randomly selected predictors (mtry) is  140, when accuracy and ROC_AUC are both accounted for. We can check this using the select_best function.
```{r, message = FALSE, warning = FALSE}
# Specify the metric and optimization criteria
best_auc <- select_best(rf_res2, metric = "roc_auc")

@@

# fit the tuned model
set.seed(123)
rf_rec <- recipe(P_UTDHPV ~ AGE + SEX + STATE + INS_STAT2_I + INCQ298A + INS_BREAK_I + INCPOV1 + RACEETHK + EDUC1 + LANGUAGE + MOBIL_1 + RENT_OWN + FACILITY, data = train_data) # use full model as recipe for the random forest model

rf_workflow <- workflow() %>% # create workflow for rf model
  add_recipe(rf_rec)%>% # apply recipe
  add_model(final_rf) # apply model

rf_tune_fit <- rf_workflow%>%
  fit(data = train_data)%>% # use the workflow to fit the rf model to the data
  print(rf_tune_fit)
```
The final random forest model was selected to optimize roc_auc, but it also has a fairly high accuracy. We can use
```{r, message = FALSE, warning = FALSE}
# make predictions
rf_tuned_aug <- augment(rf_tune_fit, train_data)

@@

Now I will compare the model will the a single predictor model and the original fit to verify that there is improvement in the predictions made.
```{r, message = FALSE, warning = FALSE}
# RF model compared to single predictor model
## Create a single model
rf_rec_null <- recipe(P_UTDHPV ~ SEX, data = train_data) # specify the model with a recipe; I could not get a null model to work so I used one predictor as a minimal model for comparison

@@

# Get predictions from single predictor model
rf_null_aug <- augment(rf_fit_null, train_data)
```
Model metrics could not be computed because there were missing classifications in the single predictor model. Because of this, I will compare the single predictor and full model using confusion matrices.
```{r}
# confusion matrix for tuned model
conf_mat(
  data = rf_tuned_aug,
  truth = P_UTDHPV,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth"),
  case_weights = NULL)

#Confusion matrix for null model
conf_mat(
  data = rf_null_aug,
  truth = P_UTDHPV,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth"),
  case_weights = NULL)
```
The confusion matrix for the tuned model (top) demonstrates that there are more false positives than false negatives. After calculating sensitivity (76.6%) and specificity(99.4%), a clear trade off between the two metrics is observed. The confusion matrix for the single predictor model (bottom) indicates that the model cannot predict an outcome of not up to date on HPV vaccination, where the NOT UTD prediction row is zero.
Finally, I will test the tuned model using the test data from the split. To make pre
```{r}
# Making predictions using test data
test_rf_aug <- augment(rf_tune_fit, test_data)

# find metrics for tuned fit
test_tuned_metrics <- metrics(truth = P_UTDHPV, estimate = .pred_class, data = test_rf_aug) # calculate metrics for first fit
print(test_tuned_metrics)
```
The tibble reveals that the accuracy and F1 measure are greatly reduced when fitting the tuned model to the test data compared to the train data. This may indicate overfitting to the train data.
Although the model is overfit, I will attempt to visualize the predictors chosen by the tuned model.
```{r}
# Finding importance of variables chosen
rf_vars <- rf_tune_fit %>%
  extract_fit_parsnip() %>% # use parsnip to extract to fit
  vip::vip() #use vip for visualizing the most important variables

print(rf_vars)
```
The most important variable, according to this model, is state, followed by income poverty ratio, then facility, then facility. Despite the importance above, it should be noted that the multicollinearity may affect the importance of the variables selected. This means that a model that regularizes the parameters could be ideal for finding the most important predictors.
For this, we will try using the LASSO model

### 2024-04-17 code/analysis-code/analysis3.qmd
Analysis of rf and lasso completed
LASSO is complete, kinda, but we could also tune the penalty to F1 instead of roc_auc and see if this improves it. Also, we could try an elastic net model if we have time. Overall rf seems to have better performance. note: changes have not been rendered

---
title: "Data Analysis and Modeling of Teen Vaccination Surveys"
date: '`r format(Sys.Date())`'
Author: Kelly Cao and Rachel Robertson
output: html_document
editor: 
  markdown: 
    wrap: sentence
---
# LASSO using Tidymodels
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
We will start by opening the libraries that we will need for creating a LASSO regression model for the data
```{r}
library(tidymodels) # use tidymodels framework
library(ggplot2) # producing visual displays of data
library(dplyr) # manipulating and cleaning data
library(here) # making relative pathways
library(glmnet) # for LASSO regression engine
library(doParallel) # for parallel processing
library(rsample) # for cross validation
library(yardstick) # for metrics
library(mlbench)

@@

```{r}
# Make predictions for the first LASSO model
predictions <- lasso_fit %>%
  augment(new_data = test_data)

@@

# Make predictions for the LASSO model with lower penalty
predictions2 <- lasso_fit2 %>%
  augment(new_data = test_data)

@@

# Make predictions for ROC_AUC with the tuned model
predictions3 <- lasso_fit3 %>%
  augment(new_data = test_data)

@@

# Cross Validation
Now we will compare the two lasso models with the penalty parameters of 0.005 and 0.01 to determine which model performs best when presented with "new data".

>>>>

---
title: "Data Analysis and Modeling of Teen Vaccination Surveys"
date: '`r format(Sys.Date())`'
Author: Kelly Cao and Rachel Robertson
output: html_document
editor: 
  markdown: 
    wrap: sentence
---
# LASSO using Tidymodels
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
We will start by opening the libraries that we will need for creating a LASSO regression model for the data
```{r}
library(tidymodels) # use tidymodels framework
library(ggplot2) # producing visual displays of data
library(dplyr) # manipulating and cleaning data
library(here) # making relative pathways
library(glmnet) # for LASSO regression engine
library(doParallel) # for parallel processing
library(rsample) # for cross validation
library(yardstick) # for metrics
library(mlbench)
library(vip)
```

@@

```{r}
# Make predictions for the first LASSO model
predictions <- lasso_fit %>%
  augment(new_data = train_data)

@@

# Make predictions for the LASSO model with lower penalty
predictions2 <- lasso_fit2 %>%
  augment(new_data = train_data)

@@

# Make predictions for ROC_AUC with the tuned model
predictions3 <- lasso_fit3 %>%
  augment(new_data = train_data)

@@

# Comparing Predictions
Now we will compare the two lasso models with the penalty parameters of 0.005 and 0.01 to determine which model performs best when presented with "new data". The new data is that split from the original data (the test data). 
```{r}
pen1_aug <- augment(lasso_fit2, test_data)
pen2_aug <- augment(lasso_fit3, test_data)
# Make find performance metrics with the tuned model
metrics <- metric_set(accuracy, f_meas) # create a set of metrics to test for classification
# Model tuned to parameter penalty = 0.005
penaltytune1 <- metrics(truth = P_UTDHPV, estimate = .pred_class, data = pen1_aug)
print(penaltytune1)
# Model tuned to parameter penalty = 0.01
penaltytune2 <- metrics(truth = P_UTDHPV, estimate = .pred_class, data = pen2_aug)
print(penaltytune2)
```
The performance metrics reveal a similar accuracy between both models, but a higher, thus better, F1 measure, from the LASSO model with the penalty of 0.005. This might indicate that, although the model tuned to the penalty 0.01 maximizes roc_auc, it may be at the cost of other performance metrics such as F1 (or precision and/or recall).
We will examine this further with confusion matrices.
```{r}
# Compare confusion matrices
# penalty 0.005
conf_mat(
  data = pen1_aug,
  truth = P_UTDHPV,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth"),
  case_weights = NULL)
# penalty 0.01
conf_mat(
  data = pen2_aug,
  truth = P_UTDHPV,
  estimate = .pred_class,
  dnn = c("Prediction", "Truth"),
  case_weights = NULL)
```
The confusion matrix for neither of these models is ideal, as they both have a fairly high number of false positives, leading to a poor sensitivity. Because the model with a lower penalty parameter seems to perform better when presented with new data, I will look at the coefficients chosen by this model and determine which variables it deems most important to predicting HPV vaccine completion.
```{r}
# Finding importance of variables chosen
lasso_vars <- lasso_fit2 %>%
  extract_fit_parsnip() %>% # use parsnip to extract to fit
  vip::vip() #use vip for visualizing the most important variables

print(lasso_vars)
```
It seems that the most important factors for HPV vaccine completion are the state, facility and housing status. The states that have the highest predictive power of HPV vaccine completion are Rhode Island, Vermont, Mississippi, and North Dakota.

Note to Kelly: Perhaps we should try tuning the penalty to a different metric. May we can try tuning to F1 and see if that produces a different penalty value?
Note to self/ Discussion idea: Maybe vaccine policy or vaccine requirements to start school differs by state, so this might affect completion rates.

### 2024-04-17 products/manuscript/Manuscript.qmd
Analysis of rf and lasso completed
LASSO is complete, kinda, but we could also tune the penalty to F1 instead of roc_auc and see if this improves it. Also, we could try an elastic net model if we have time. Overall rf seems to have better performance. note: changes have not been rendered

# Methods

## Data Cleaning and Processing

### Loading the data

The data was loaded from the original DAT file, entitled 'NISTEENPUF22.DAT' by specifying the column positions within the data file.
The columns were then read and made into a data frame.
Next, each of the factor variables were defined and the corresponding levels were assigned labels.
The structure and summary statistics of all of the variables were examined.
The loaded data is saved as a rds and a csv in the 'processed-data' folder.
This does not alter the original raw data file.
The definition of each factor variable in included in the README file within the 'raw-data' folder.

Next, we explored the structure of the processed data and searched for any missing values.
However, there were no NAs present.
There are, however, missing values as labelled factor levels which must be accounted for.
We identified the missing value labels by printing the factor levels.
We then replaced the all of the values labelled missing with NA values.
Next, we found a string of over 27000 NAs all of the variables for vaccination completion.
These rows corresponded for all variables related to vaccine completion.
Since this is the response variable of our scientific question, we eliminated these rows.
We also eliminated rows with small numbers missing values, which were within the columns for facility, Wellchild exams, and insurance breaks.
Lastly, we eliminatethe year column, as all of the data comes from the year 2022.
We saved the cleaned data as an rds and csv in the 'processed-data' folder.

## Exploratory Analysis

We use our exploratory analysis to determine the distribution of our predictors, including the socioeconomic variables that we chose for analysis.
The overall distribution of each factor variable is shown below.

```{r}
#| label: Table1
#| tbl-cap: "Table 1.Socioeconomic characteristics of U.S. teenagers who have completed or are up-to-date with HPV vaccination series."
#| echo: FALSE
Table1 <- readRDS(here("results/tables/table1.rds"))
kable(Table1)
```
```

The distribution of the numerical income to poverty ratio can be shown below.
It displays a value from 1-3.
A ratio displaying less than 1 depicts an income less than the poverty level.Any income ratio \>1 indicates an income greater than the poverty level.
Most of the observations were gathered from households with income ratios of 3, as shown by the skewed plot below.

@@

# Analysis

@@

>>>>

# Methods
## Loading Data
The data was loaded from the original DAT file, entitled 'NISTEENPUF22.DAT' by specifying the column positions within the data file. The columns were then read and made into a data frame. Each of the factor variables was defined and the corresponding levels were assigned labels. The structure and summary statistics of all of the variables were examined. The loaded data is saved as a rds and a csv in the 'processed-data' folder, as to not alter the original raw data file. The definition of each factor variable in included in the README file within the 'raw-data' folder.

## Cleaning Data
The structure of the processed data was examined.  The data was examined for missing values. No NAs were present, however missing values were present as labeled factor levels. The missing factor levels were printed, identified, and replaced with NA values. A string of 27,000 NAs were present in the outcome variable, indicating vaccination completion. All rows corresponding to the NAs for the missing outcome value were removed. Approximately 160 additional rows with NA values for facility or insurance status variables were removed. Over 16,000 rows of data remained. The year column was eliminated, as all of the data is from 2022. We saved the cleaned data as an rds and csv in the 'processed-data' folder.
## Exploratory Analysis
Exploratory analysis was used to determine the distribution of the predictors, including the socioeconomic variables that were chosen for analysis. The distribution of single predictors including income-to-poverty ratio, income, state, race, ethnicity, vaccination status, and facility were examined using histograms and scatter plots. The following predictors were compared visually and fitted to a linear regression to examine preexisting associations: vaccination status and ethnicity, vaccination status and poverty status, income poverty ratio and insurance status, income poverty ratio and ethnicity. 
## Analysis
### Generalized Logistic Regression
A generalized logistic regression was performed with bi-directional step-wise selection for predictor reduction. Variables that were redundant of a major variable were excluded from analysis. The variables initially included were age, sex, state, race/ethnicity, insurance status, income, insurance breaks, poverty status, education, language, geographic mobility, facility, and housing status. The model was evaluated with a residual plot and correlation matrix to reveal strong multicollinearity. This is the basis for the subsequent analysis methods, as they are more resistant to collinearity.
### Principal Component Analysis
Principal component analysis (PCA) was performed to do dimensionality reduction. PCA would ideally transform the highly correlated predictors into uncorrelated components. The h2o package was used to provide a machine-learning platform in RStudio, to allow machine-learning methods ot be implemented. Due to the data being mainly categorical variables, the PCA proved to be unsuccessful. A LASSO Ridge Regression was performed with the h2o package, to mitigate the multicollinearity issue.
### Random Forest Model
A random forest model was used, as it is resistant to multicollinearity. The tidymodels package was used to produce a random forest model with the classification method. The model was trained and fit from training data, which was an 80% split of the original data. After evaluation, the model parameters for minimal node size and number of selected predictors were tuned for using a grid search with cross-validation resamples. After tuning, the best model was extracted based on the ROC AUC metric and was fit to the training data. The tuned model was used to make predictions and evaluated with performance metrics, a confusion matrix, and a comparison to a single-predictor random forest model. Finally, the tuned random forest model was re-evaluated by being fit to the testing data.
### LASSO Regression

# Results
## Exploratory Data Analysis
Exploratory analysis is used to determine the distribution of our predictors, including the socioeconomic variables that we chose for analysis. Nearly all of the demographic factors have a similar distribution between those who have completed their HPV vaccination regime versus those who have not completed it.

```{r}
#| label: Table1
#| tbl-cap: "Table 1.Socioeconomic characteristics of U.S. teenagers who have completed or are up-to-date with HPV vaccination series."
#| echo: FALSE
Table1 <- readRDS(here("results/tables/table1.rds"))
kable(Table1)
```
The distribution of the numerical income to poverty ratio can be shown below.
It displays a value from 1-3.
A ratio displaying less than 1 depicts an income less than the poverty level.Any income ratio \>1 indicates an income greater than the poverty level.
Most of the observations were gathered from households with income ratios of 3, as shown by the skewed plot below.

@@

## Analysis

@@

# Discussion

# Conclusion
